Figures

### 2019-11-12 manuscript/figures.Rmd
phenotypic descriptor info table added to plan

```{r siteLocations,fig.cap='Map showing locations of the nine sites used for collection of phenotypic descriptors.',fig.width=3,fig.height=5}
source('../R/figures/site_locations.R')
site_locations_map
```

>>>>

```{r siteLocations,fig.cap='Map showing locations of the nine sites used for collection of phenotypic descriptors.',fig.width=3,fig.height=5}
source('../code/figures/site_locations.R')
site_locations_map
```
